fig4

### 2020-02-11 analysis/figure-4.Rmd
now with top 3 genes

hypgenes <- read_csv("../results/DEseq2/female_hypothalamus_hatch_n5_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 2) %>% pull(gene)
hypgenes

pitgenes <- read_csv("../results/DEseq2/female_pituitary_inc.d9_inc.d17_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 2) %>% pull(gene)
pitgenes

gongenes <- read_csv("../results/DEseq2/female_gonad_lay_inc.d3_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 2) %>% pull(gene)
gongenes

>>>>

hypgenes <- read_csv("../results/DEseq2/female_hypothalamus_hatch_n5_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 3) %>% pull(gene)
hypgenes

pitgenes <- read_csv("../results/DEseq2/female_pituitary_inc.d9_inc.d17_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 3) %>% pull(gene)
pitgenes

gongenes <- read_csv("../results/DEseq2/female_gonad_lay_inc.d3_DEGs.csv") %>%
  arrange(desc(logpadj)) %>% head(., n = 3) %>% pull(gene)
gongenes
